---
title: "Final Project- Repeatable Experiments"
subtitle: "726 Theory of Statistics II"
author: "Rebecca Kotula"
output: pdf_document
---

## Load Packages and Data

```{r, warning=FALSE}
library(tidyverse)
library(stopwords)
library(tm)
library(topicmodels)
library(tidytext)
library(ggwordcloud)
library(ggthemes)
library(ldatuning)
library(reshape)
library(wesanderson)
library(lda)
library(ramify)

theme_set(theme_tufte())

filepath <- "~/Library/Mobile Documents/com~apple~CloudDocs/Documents/JHU/Theory of Statistics II/Project/blogtext.csv"
data <- read.csv(filepath)

data <- data[,c(1,7,4)]
colnames(data) <- c("doc_id", "text", "topic")
data <- data[data$topic != "indUnk",]
data <- data[data$topic != "Student",]
set.seed(1234)
data <- sample_n(data, 10000)
```

## Plot topic distribution

```{r}
h <- ggplot(data, aes(x=topic)) + geom_bar(fill='olivedrab')+ theme_tufte() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    ylab("Document Count") + xlab("Topic") 
h
```

## Data Cleaning

```{r}
prepare_data <- function(data) {
    docs <- Corpus(DataframeSource(data)) %>%
        tm_map(removePunctuation) %>%
        tm_map(content_transformer(tolower)) %>%
        tm_map(removeNumbers) %>%
        tm_map(removeWords, stopwords("english")) %>%
        tm_map(removeWords, "urllink") %>%
        tm_map(stripWhitespace)
    return(docs)
}
```

## Document-Term Matrix

```{r}
docs <- prepare_data(data)

dtm <- DocumentTermMatrix(docs, control=list(bounds = list(global = c(2,Inf))))
dtm <- removeSparseTerms(dtm, 0.99)

#Remove empty rows from Vocabulary pruning (from DTM and docs)
keep.idxs=rowSums(as.matrix(dtm)) > 0
dtm <- dtm[keep.idxs,]
data <- data[keep.idxs,]
```

### Find Topics Number

This parameter search was, in practice, broken down into smaller chunks for computational feasibility (meaning that the whole search from 30 through 70 was not performed in one run).

```{r}
result <- FindTopicsNumber(
  dtm,
  topics = seq(from = 30, to = 70, by = 2),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"), 
  method = "Gibbs",
  control = list(seed = 1234),
  mc.cores = 2L,
  verbose = TRUE
)
```

```{r}
FindTopicsNumber_plot(full_result)
```

## Fit Selected Models

```{r}
#Selected # of topics for each model:
# Baseline 38
# Griffiths, Arun 70
# Cao 68
# Deveaud 52

seed <- 1234
k <- c(38, 52, 68, 70)
lda38 <- LDA(dtm, k[1], method="Gibbs", control=list(seed = seed,verbose=25))
lda52 <- LDA(dtm, k[2], method="Gibbs", control=list(seed = seed,verbose=25))
lda68 <- LDA(dtm, k[3], method="Gibbs", control=list(seed = seed,verbose=25))
lda70 <- LDA(dtm, k[4], method="Gibbs", control=list(seed = seed,verbose=25))


#topic.top.terms <- terms(ldaOut,25)
```

## Sample Document Topic Proportions

```{r}
# create descriptive topic names from characteristic words
beta38 <- posterior(lda38)$terms
theta38 <- posterior(lda38)$topics
topicNames38 <- apply(top.topic.words(beta38, 5, by.score = T), 2, paste, collapse = " ")

beta52 <- posterior(lda52)$terms
theta52 <- posterior(lda52)$topics
topicNames52 <- apply(top.topic.words(beta52, 5, by.score = T), 2, paste, collapse = " ")

beta68 <- posterior(lda68)$terms
theta68 <- posterior(lda68)$topics
topicNames68 <- apply(top.topic.words(beta68, 5, by.score = T), 2, paste, collapse = " ")

beta70 <- posterior(lda70)$terms
theta70 <- posterior(lda70)$topics
topicNames70 <- apply(top.topic.words(beta70, 5, by.score = T), 2, paste, collapse = " ")

```

```{r}
docs.sample <- c(20, 77, 1505)
n <- length(docs.sample)

#sample.text <- data[docs.sample,]
#sample.text$text
```

```{r}
#lda38
topics.in.docs <- theta38[docs.sample,]
colnames(topics.in.docs) <- topicNames38
plot.df <- melt(cbind(data.frame(topics.in.docs), document = factor(1:n)), id.vars = "document")  
ggplot(data = plot.df, aes(variable, value, fill = document)) + 
    geom_bar(stat="identity") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
    coord_flip() +
    labs(x="Topic", y="", title="LDA with 38 Topics")+
    facet_wrap(~ document, ncol = n) + 
    scale_fill_manual(values=wes_palette("Darjeeling1", n=n))
#ggsave("~/Library/Mobile Documents/com~apple~CloudDocs/Documents/JHU/Theory of Statistics II/Project/final_images/lda38_doc_topic_sample.png", height=8)
```

```{r}
#lda52
topics.in.docs <- theta52[docs.sample,]
colnames(topics.in.docs) <- topicNames52
plot.df <- melt(cbind(data.frame(topics.in.docs), document = factor(1:n)), id.vars = "document")  
ggplot(data = plot.df, aes(variable, value, fill = document)) + 
    geom_bar(stat="identity") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
    coord_flip() +
    labs(x="Topic", y="", title="LDA with 52 Topics")+
    facet_wrap(~ document, ncol = n) + 
    scale_fill_manual(values=wes_palette("Darjeeling1", n=n))
#ggsave("~/Library/Mobile Documents/com~apple~CloudDocs/Documents/JHU/Theory of Statistics II/Project/final_images/lda52_doc_topic_sample.png", height = 8)
```

```{r}
#lda68
topics.in.docs <- theta68[docs.sample,]
colnames(topics.in.docs) <- topicNames68
plot.df <- melt(cbind(data.frame(topics.in.docs), document = factor(1:n)), id.vars = "document")  
ggplot(data = plot.df, aes(variable, value, fill = document)) + 
    geom_bar(stat="identity") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
    coord_flip() +
    labs(x="Topic", y="", title="LDA with 68 Topics")+
    facet_wrap(~ document, ncol = n) + 
    scale_fill_manual(values=wes_palette("Darjeeling1", n=n))
#ggsave("~/Library/Mobile Documents/com~apple~CloudDocs/Documents/JHU/Theory of Statistics II/Project/final_images/lda68_doc_topic_sample.png", height = 9)
```

```{r}
#lda70
topics.in.docs <- theta70[docs.sample,]
colnames(topics.in.docs) <- topicNames70
plot.df <- melt(cbind(data.frame(topics.in.docs), document = factor(1:n)), id.vars = "document")  
ggplot(data = plot.df, aes(variable, value, fill = document)) + 
    geom_bar(stat="identity") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
    coord_flip() +
    labs(x="Topic", y="", title="LDA with 70 Topics")+
    facet_wrap(~ document, ncol = n) + 
    scale_fill_manual(values=wes_palette("Darjeeling1", n=n))
#ggsave("~/Library/Mobile Documents/com~apple~CloudDocs/Documents/JHU/Theory of Statistics II/Project/final_images/lda70_doc_topic_sample.png", height=9)
```

## Get most common topics from each model

```{r}
topic_props38 <- colSums(theta38)/nDocs(dtm)
names(topic_props38) <- topicNames38
top5_topics38 <- sort(topic_props38, decreasing=TRUE)[0:5]

topic_props52 <- colSums(theta52)/nDocs(dtm)
names(topic_props52) <- topicNames52
top5_topics52 <- sort(topic_props52, decreasing=TRUE)[0:5]

topic_props68 <- colSums(theta68)/nDocs(dtm)
names(topic_props68) <- topicNames68
top5_topics68 <- sort(topic_props68, decreasing=TRUE)[0:5]

topic_props70 <- colSums(theta70)/nDocs(dtm)
names(topic_props70) <- topicNames70
top5_topics70 <- sort(topic_props70, decreasing=TRUE)[0:5]

top5_topics_all_models <- data.frame()
top5_topics_all_models[1:5,"lda38"] <- names(top5_topics38)
top5_topics_all_models[1:5, "lda52"] <- names(top5_topics52)
top5_topics_all_models[1:5,"lda68"] <- names(top5_topics68)
top5_topics_all_models[1:5,"lda70"] <- names(top5_topics70)
#write.csv(top5_topics_all_models, "~/Library/Mobile Documents/com~apple~CloudDocs/Documents/JHU/Theory of Statistics II/Project/top_topics.csv", row.names=FALSE)

```

## T-SNE

```{r}
library(Rtsne)
dtm.matrix <- data.frame(as.matrix(dtm))
data.sub <- data[!duplicated(dtm.matrix),]
dtm.matrix <- dtm.matrix[!duplicated(dtm.matrix),]
tsne_out <-Rtsne(dtm.matrix)
```

```{r}
t_dat <- data.frame(tsne_out$Y)
t_dat$topic <- data.sub$topic
t <- ggplot(t_dat)+ geom_point(aes(x=X1,y=X2, col=topic))
t
#ggsave("./final_images/tsne.png", width=8, height=6)
```

## Scoring Metric

Checking if topic labels appear in top 100 words from LDA topics (they do not....)

```{r}
topicwords38 <- top.topic.words(beta38, 100, by.score=T)
topicwords52 <- top.topic.words(beta52, 100, by.score=T)
topicwords68 <- top.topic.words(beta68, 100, by.score=T)
topicwords70 <- top.topic.words(beta70, 100, by.score=T)


#top.topic <- argmax(theta38)

score38 <- 0
score52 <- 0
score68 <- 0
score70 <- 0
for (i in range(length(data))){
    if (tolower(data$topic[i]) %in% topicwords38[,top.topic[i]]){
        score38 <- score38 + 1
    }
    if (tolower(data$topic[i]) %in% topicwords52[,top.topic[i]]){
        score52 <- score52 + 1
    }
    if (tolower(data$topic[i]) %in% topicwords68[,top.topic[i]]){
        score70 <- score68 + 1
    }
    if (tolower(data$topic[i]) %in% topicwords70[,top.topic[i]]){
        score70 <- score70 + 1
    }
}
print(score38)
print(score52)
print(score68)
print(score70)

topics <- unique(data$topic)
topics.in.38 <- 0
topics.in.52 <- 0
topics.in.68 <- 0
topics.in.70 <- 0

for (i in range(length(topics))){
     if (tolower(topics[i]) %in% topicwords38){
         topics.in.38 <- topics.in.38 + 1
     }
    if (tolower(topics[i]) %in% topicwords52){
         topics.in.52 <- topics.in.52 + 1
    }
    if (tolower(topics[i]) %in% topicwords68){
         topics.in.68 <- topics.in.68 + 1
    }
    if (tolower(topics[i]) %in% topicwords70){
         topics.in.70 <- topics.in.70 + 1
     }
}
print(topics.in.38)
print(topics.in.52)
print(topics.in.68)
print(topics.in.70)
```
